An Open System for\\ Managing Short Programming Exercises

### 2013-08-08 paper/talk.tex
tweaks to questions
hosting slide

\begin{itemize}
  \item Open source (AGPL v3)
  \item Supports exercises in Java, Python, Ruby, and C/C++
  \item Collects fine-grained edit sequence of each student's work
  \item Repository of freely-redistributable (CC-BY-SA) exercises:
        \url{https://cloudcoder.org/repo}
  \item Requires two Linux servers to host (one network-facing)
    \begin{itemize}
    \item Relatively easy to install
    \item Known to support 60+ concurrent users with modest hardware
    \item Load testing experiments successful with 700+ concurrent users
          on moderate server hardware
      \begin{itemize}
      \item Compiling and testing submissions requires significant
            CPU resources, but is easy to scale up by adding more
            build servers
      \end{itemize}
    \item Cost to host per course-semester: perhaps \$1-\$3 per student
          (e.g., using Amazon EC2)
    \end{itemize}
\end{itemize}

@@

\begin{itemize}
\item Are short exercises useful?
  \begin{itemize}
  \item What experiments should we do to find out?
  \end{itemize}
\item How do we most effectively incorporate short exercises into a course?
  \begin{itemize}
  \item How do we know what exercises to use?
  \item What mix of short exercises vs.\ larger assignments?
  \end{itemize}
\end{itemize}

>>>>

\begin{itemize}
  \item Open source (AGPL v3)
  \item Supports exercises in Java, Python, Ruby, and C/C++
  \item Collects fine-grained edit sequence of each student's work
  \item Repository of freely-redistributable (CC-BY-SA) exercises:
        \url{https://cloudcoder.org/repo}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%% CloudCoder screenshot %%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Hosting CloudCoder}

\begin{itemize}
  \item Requires two Linux servers to host (one network-facing)
    \begin{itemize}
    \item Relatively easy to install
    \item Known to support 60+ concurrent users with modest hardware
    \item Load testing experiments successful with 700+ concurrent users
          on moderate server hardware
      \begin{itemize}
      \item Compiling and testing submissions requires significant
            CPU resources, but is easy to scale up by adding more
            build servers
      \end{itemize}
    \item Cost to host per course-semester: perhaps \$1-\$3 per student
          (e.g., using Amazon EC2)
    \end{itemize}
  \item {\bf We can host CloudCoder for your course!}
    \begin{itemize}
    \item We have a grant from Amazon to cover hosting costs for
          a small number of institutions/courses
    \item {\bf Talk to us if you are interested!}
    \end{itemize}
\end{itemize}

@@

\begin{itemize}
\item Are short exercises useful?
  \begin{itemize}
  \item Would {\em you} want to use short exercises in your course?
  \item What experiments should we do to measure effect on outcomes?
  \end{itemize}
\item How do we most effectively incorporate short exercises into a course?
  \begin{itemize}
  \item How do we know what exercises should be assigned?
  \item In what order should the exercises be assigned?
  \item What mix of short exercises vs.\ larger assignments?
  \end{itemize}
\end{itemize}
